---
title: "ZoomCorrelation Examples"
output: html_document
date: "2024-11-27"
---

```{r setup, include=FALSE}
library(ZoomCorrelation)
```

## ZoomCorrelation Function Examples

This document demonstrates the usage of the zoom_correlation function with different types of correlations and zoom levels.

## Create data with perfect positive correlation
This example demonstrates a dataset with a perfect positive correlation, where the y variable is directly proportional to the x variable.
```{r perfect_correlation}
test_perfect <- data.frame(
    x = 1:100,
    y = 2 * (1:100)
)
zoom_correlation(test_perfect, "x", "y")
```

## Different Zoom Levels
Here we demonstrate how changing the zoom_factor parameter affects the intensity of the zoom effect.
```{r zoom_levels}
# More intense zoom (zoom_factor = 0.02)
zoom_correlation(test_perfect, "x", "y", zoom_factor = 0.02)

# Less intense zoom (zoom_factor = 0.10)
zoom_correlation(test_perfect, "x", "y", zoom_factor = 0.10)
```

## Perfect Negative Correlation
This example demonstrates a dataset with a perfect negative correlation, where the y variable is inversely proportional to the x variable.
```{r negative_correlation}
# Create data with perfect negative correlation
test_negative <- data.frame(
    x = 1:100,
    y = -2 * (1:100)
)
zoom_correlation(test_negative, "x", "y")
```

## Strong but Imperfect Correlation
Here we simulate a dataset with a strong but imperfect positive correlation. Random noise is added to the y variable.
```{r strong_correlation}
#Create data with strong but imperfect correlation
test_strong <- data.frame(
    x = 1:100,
    y = 2 * (1:100) + rnorm(100, sd = 5)
)
zoom_correlation(test_strong, "x", "y")
```

## Weak Correlation
This example demonstrates a dataset with weak correlation, where the relationship between x and y is almost random.
```{r weak_correlation}
## Create data with weak correlation
test_weak <- data.frame(
    x = 1:100,
    y = rnorm(100)
)
zoom_correlation(test_weak, "x", "y")
```
Each example demonstrates different aspects of the zoom_correlation function, from perfect correlations to weak correlations, and shows how the zoom effect changes based on the correlation strength.
